---
title: "Homework1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import data from yahoo finance
install.packages("quantmod")

# Import data from yahoo finance
```{r, include = TRUE}
rm(list=ls())
library(quantmod)
getSymbols("GOOG", auto.assign = TRUE)
```
# There are two primary time series data xts and zoo

```{r}
tickers = c("GOOG", "MSFT", "AMZN")
getSymbols(tickers, from = "2010-01-01", auto.assign = TRUE)
```
# Download multiple prices to data variable

```{r}
data = new.env()
getSymbols(tickers, from = "2010-01-01", env = data , auto.assign = TRUE)
ls(data)
names(data)
head(data$AMZN)
```
```{r, include =TRUE}
str(AMZN)
class(AMZN)
tail(AMZN,3)
names(AMZN)
ls(AMZN)
head(AMZN$AMZN.Close)
AMZN2010_15=AMZN['2010/2015']
```
### Extract closing price: Cl() 
### Adjusted price: Ad()
```{r}
AMZN.ad<-Ad(AMZN)
head(AMZN.ad)
class(AMZN.ad)
```
# Write function to gather adjusted prices together
```{r}
firm3<-merge(Ad(AMZN), Ad(GOOG), Ad(MSFT))
head(firm3)
colnames(firm3)<-c("AMZN", "GOOG", "MSFG")
head(firm3)
```
```{r}
# Import data from .txt file
etf4<-read.table("ETF4_2010_2018_d1_english.txt", header = T, sep = ',')
str(etf4)
```
```{r}
# convert CO_ID into character;
etf4<-read.table("ETF4_2010_2018_d1_english.txt", header = T, sep = ',',
                 colClasses = c("CO_ID" = "character"))
str(etf4)
head(etf4)
write.csv(etf4, "etf4.csv")
```
install.packages("readr")
```{r}
library(readr)
etf4_csv<-read.csv("etf4.csv")
etf4_csv
```
#--------------------------
# Clean data
```{r}
etf4.c<-etf4_csv[, c(-1,-3,-6)]
etf4.c
colnames(etf4.c)<-c("id", "date", "price")
etf4.c
```
# Use pipe operator
install.packages("magrittr")
```{r}
library(magrittr)
```
#install.packages("dplyr")
install.packages("dplyr")
```{r}
library(dplyr)
etf4.c<-etf4_csv%>%select(c(2,4,5))%>%rename("id" = "CO_ID", "date"= "Date", "price" = "Close")
etf4.c
```
#-----------------------------------------------------------------              
# Use dcast to reorder dataframe by date
install.packages("reshape2")
```{r}
library(reshape2)
etf4.reorder = dcast(etf4.c, date~id)
dim(etf4.reorder)
head(etf4.reorder)
str(etf4.reorder)
```
# Convert into date format using as.Date()
'''{r}
etf4.reorder$date<-as.Date(as.character(etf4.reorder$date), "%Y%m%d") 
head(etf4.reorder)
str(etf4.reorder)
'''
# Convert character into numeric 
# Convert to xts
install.packages("xts")
```{r}
library(xts)
etf4.xts<-xts(etf4.reorder[,-1], order.by = etf4.reorder$date)
head(etf4.xts)
tail(etf4.xts)
str(etf4.xts)
```
# Convert into date format using as.Date()
```{r}
etf4.reorder$date<-as.Date(as.character(etf4.reorder$date), "%Y%m%d") 
head(etf4.reorder)
str(etf4.reorder)
```
